BivData Setup

### 2020-02-19 src/BivData_Setup.Rmd
smllchanges
added rec.group col to main bivData DF

add Q1 and Q4 to the cell summary stats table

@@

@@

<!--
I'm considering removing the same mice from the MLH1 counts, from the BivData, but this might -- limit the comparisons -- might be too stict. IF foci are bright and clear, SC/bivalents intact -- include.

@@

- the reasons for poor quality of the exclude mice in above list, might be from 2-3 bad bivalents -- which are removed from the biv data during the curation process. 
-->

@@

)
```

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_13.2.20.RData")
#save.image("data/BivData_4_PCA.RData")

>>>>

@@

#add rec.group
#divide musc males into groups
Curated_BivData$Rec.group <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
                                  ifelse(grepl("MSM male", Curated_BivData$category), 1,
                                  ifelse(grepl("SKIVE male", Curated_BivData$category), 1,
                                           0)))

Curated_BivData$Rec.group.exclu <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
                                ifelse(grepl("MSM male", Curated_BivData$category), 1, 0))

@@

I'm considering removing the same mice from the MLH1 counts, from the BivData, but this might -- limit the comparisons -- might be too stict. IF foci are bright and clear, SC/bivalents intact -- include.

@@

- the reasons for poor quality of the exclude mice in above list, might be from 2-3 bad bivalents -- which are removed from the biv data during the curation process.

@@

#add all the other calculations

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_19.2.20.RData")
#save.image("data/BivData_4_PCA.RData")
